%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Abhigyan — Resume (1-page variant)
% Built with Trey Hunner's resume.cls
% CONTENT UNCHANGED — only spacing + skills reimagination
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,letterpaper]{resume}

% Tighter margins + 10pt to claw back vertical space
\usepackage[left=0.55in,top=0.25in,right=0.55in,bottom=0.25in]{geometry}

% Trim whitespace
\usepackage[parfill]{parskip}
\setlength{\parskip}{2pt}
\linespread{1.05}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

% --- Tighten section heading block (default: \bigskip + \medskip) ---
\renewcommand{\sectionskip}{\vspace{4pt}}
\renewcommand{\sectionlineskip}{\vspace{2pt}}

% --- Tighten name + address block ---
\renewcommand{\nameskip}{\vspace{-2pt}}
\renewcommand{\addressskip}{\vspace{-2pt}}

% --- Tighter job-block (rSubsection): reduce inter-item gap and trailer space ---
\makeatletter
\AtBeginDocument{%
  \renewenvironment{rSubsection}[4]{%
    \textbf{#1} \hfill #2%
    \ifthenelse{\equal{#3}{}}{}{\\[-2pt] \emph{#3} \hfill \emph{#4}}%
    \vspace{-2pt}%
    \begin{list}{$\cdot$}{\leftmargin=1em%
      \setlength{\itemsep}{0pt}%
      \setlength{\parsep}{0pt}%
      \setlength{\topsep}{0pt}%
    }\item[]%
  }{\end{list}\vspace{2pt}}%
}
\makeatother

\name{Abhigyan}
\address{abhigyan0987@gmail.com \quad $|$ \quad +91-7****-****7 \quad $|$ \quad github.com/abster12}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Indian Institute of Technology (B.H.U), Varanasi} \hfill {\em July 2016 -- July 2020} \\
Bachelor of Technology (B.Tech)
\end{rSection}

%----------------------------------------------------------------------------------------
%	SKILLS  (reimagined as a single compact line)
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}
{\bf Backend \& Systems:} Spring Boot, Dropwizard, Kafka, Java, Python, Workflow Engines \par
{\bf Cloud \& Data:} AWS, Docker, Kubernetes, MySQL, ELK, CI/CD \par
{\bf AI \& LLM:} RAG, Multi-Agent Systems, Milvus, Claude Code, Cursor, Windsurf
\end{rSection}

%----------------------------------------------------------------------------------------
%	EXPERIENCE  (content unchanged from your original)
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Walmart}{May 2024 -- Present}{Software Engineer 3}{}
\item Led performance optimization of core \textbf{Start and Update Workflow APIs}, reducing \textbf{P95 latency from \textasciitilde200ms to \textasciitilde130ms} and scaling the platform to \textbf{\textasciitilde1500 synchronous workflow executions per second} through database query optimizations and infrastructure tuning.
\item Designed and implemented a \textbf{multi-tenant onboarding architecture} supporting multiple teams and \textbf{multiple workflow engines per tenant} within a shared cluster, defining data models, relationships, and lifecycle management.
\item Owned the \textbf{end-to-end integration of Orkes Workflow Engine}, enabling \textbf{workflow-driven orchestration across backend and AI-powered systems}, including SDK integration, configuration management, and runtime interoperability.
\item Built and owned a \textbf{production-grade AI platform}, including RAG pipelines (Docling, pdfplumber, Vision LLMs), \textbf{hybrid retrieval using Milvus (semantic + BM25 with RRF and cross-encoder re-ranking)}, and LLM-based response generation with evaluation and observability pipelines.
\item Designed and implemented a \textbf{stateful multi-agent orchestration system} with task decomposition, parallel execution, dynamic model selection, and \textbf{persisted workflow state for deterministic pause/resume}, enabling human-in-the-loop code generation and review cycles.
\item Built internal \textbf{AI-powered developer tooling} and introduced \textbf{spec-driven development workflows using LLMs}, improving engineering velocity and consistency across feature development.
\item Mentored a junior engineer while owning services end-to-end within a \textbf{6-member backend team}, contributing to design reviews and technical decisions.
\end{rSubsection}

\begin{rSubsection}{Rakuten}{May 2023 -- May 2024}{Software Engineer 2}{}
\item Designed high-volume payment batch processing systems and APIs, enabling seamless third-party integrations across multiple Rakuten brands.
\item Built a Java-based mock server framework to simulate external payment providers, improving integration test coverage and reliability.
\end{rSubsection}

\begin{rSubsection}{Podeum}{July 2022 -- May 2023}{Founding Engineer}{}
\item Built and scaled backend services from scratch using Java, supporting growth from \textbf{0 to \textasciitilde10,000 daily active users}.
\item Designed and implemented core platform systems including authentication, virtual economy, in-app purchases, and real-time live score feeds.
\end{rSubsection}

\begin{rSubsection}{Morgan Stanley, Bangalore}{Oct 2020 -- Jun 2022}{Software Developer}{}
\item Developed and maintained Big Data applications and set up CI/CD pipelines with Jenkins and Sonar, improving code quality and deployment workflows.
\end{rSubsection}

\end{rSection}

\end{document}
